Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{Identify applicable funding agency here. If none, delete this.}

### 2023-05-16 paper-2023-acsos-pulverization.tex
keywords: +deployment
fix snippet 1

\begin{IEEEkeywords}
runtime reconfiguration, distributed systems, self-adaptation, self-organisation, pulverisation
\end{IEEEkeywords}

@@

From the previous section,
we can identify two main phases in the pulverisation process:
\begin{enumerate*}[label=\it{(\roman*)}]
  \item the definition of the available devices and their capabilities (\emph{infrastructure}); and
  \item the allocation of the pulverised components to them (\emph{runtime}).
\end{enumerate*}
%
Coherently with the single responsibility principle,
we decided to capture these phases into two distinct \acp{dsl}.

The infrastructure \ac{dsl} captures the concepts of
\emph{logical device}, \emph{component}, \emph{capability}, and \emph{requirement}.
%
The DSL enables the definition of the type of devices that took part in the system,
and for each device can be specified which components constitute it and where those component must run on (e.g. which host must execute the component).
%
The execution of a component is constrained to hosts with predetermined characteristics:
the framework models the constraint with the \texttt{Capability} concept,
namely the property that a host must to ``implement'' to run the component.
%
Different capabilities can be specified for each component to provide a more flexible and scalable deployment of the system.

>>>>

\begin{IEEEkeywords}
runtime reconfiguration, distributed systems, self-adaptation, self-organisation, pulverisation, deployment.
\end{IEEEkeywords}

@@

From the previous section,
we can identify two main phases in the pulverisation process:
\begin{enumerate*}[label=\it{(\roman*)}]
  \item the definition of the available devices and their capabilities (\emph{infrastructure}); and
  \item the allocation of the pulverised components to them (\emph{runtime}).
\end{enumerate*}
%
Coherently withush the single responsibility principle,
we decided to capture these phases into two distinct \acp{dsl}.

The infrastructure \ac{dsl} captures the concepts of
\emph{logical device}, \emph{component}, \emph{capability}, and \emph{requirement}.
%

The DSL enables the definition of the type of devices that take part in the system,
and for each device can be specified which components constitute it and where those component must run on (e.g. which host must execute the component).
%
The execution of a component is constrained to hosts with predetermined characteristics:
the framework models the constraint with the \texttt{Capability} concept,
namely the property that a host must to ``implement'' to run the component.
%
Different capabilities can be specified for each component to provide a more flexible and scalable deployment of the system.
